---
title: "Initial Korean covid 19"
author: "David"
date: "NOV,1"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
kRdata <- kRdata %>%
mutate(across(where(is.character), as.factor))

```
### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 2020
### This data was retrieved from a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   

```{r}
str(kRdata)
```

  
# Your Question - Is dying independent of sex?
$H_0$: I have no idea, I'll see you in the Spring semester
$H_A$: If i include a $50 bill in my final assignment, will i pass.


## Method
Since we are comparing $result to $sex, we then are going to use Cat~Cat 

## Graphical results - use ggplot commands to do this  

```{r}
dd2 <- kRdata %>% group_by(result,Sex) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())

basicC <- ggplot(dd2,aes(x=Sex,y=count,fill=result))
basicC + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCC <- ggplot(dd2,aes(x=Sex,y=prcnt*100,fill=result)) 
basicCC + geom_bar(stat="identity", position = "dodge")
```

the graph shows than men have a higher chance of dying than women in Korea from covid.

### Numerical Summaries  

```{r}
table1 <- xtabs(~result + Sex, data=kRdata)
rowPerc(table1)
colPerc(table1)
```
The data above shows that your more prone to dying to covid as a male than a female.



## Inferential

```{r}
chisq.test(table1)
chisqtestGC(table1)
```

we get a p-value of 0.0012, which is smaller than 0.05, meaning there is a correlation between death and sex.

```{r}
fisher.test(table1)
```

with this test, we get a p-value of 9e-04 (.0009) which is smaller than 0.05, which also means a correlation between death and sex. you have a 2.3 to 1 odds of dying from covid as a male than a female.

## Conclusions

is there a correlation between death and sex. well yes there is as we find out that there is a correlation between death and sex. how its a greater chance that you die from covid as a male than a female in Korea.  

